Homework 4

### 2013-02-19 hw4/document/hw4.tex
Added the word cloud
Fixed minor stuff

\title{Homework 4}
\author{Caius Brindescu \and Mihai Codoban \and Semih Okur \and Shao Yuan \and Kyungho Leoo}

@@

\begin{figure}
	\begin{center}
		\includegraphics{image.jpg}
	\end{center}
	\caption{The image we used}
	\label{fig:image}
\end{figure}

\begin{figure}
	%%\includegraphics{cloud.png}
	\caption{The word cloud}
	\label{fig:cloud}
\end{figure}

@@

@@

By getting first impressions, we align ourselves with the global perception. When working in the studio, it is easy to get a skewed perception, to derail from the global train of thought. By getting valuable feedback from the outsied, we align ourselves once more with reality.

>>>>

\title{Homework 4}
\author{Caius Brindescu \and Mihai Codoban \and Semih Okur \and Shao Yuan \and Kyungho Lee}

@@

\begin{figure}[hbt]
	\begin{center}
		\includegraphics{image.jpg}
	\end{center}
	\caption{The image we used}
	\label{fig:image}
\end{figure}

\begin{figure}[hbt]
	\includegraphics[width=\textwidth]{wordcloud.png}
	\caption{The word cloud}
	\label{fig:cloud}
\end{figure}

@@

As the word cloud shows, it actually converged to the core concept.

@@

By getting first impressions, we align ourselves with the global perception. When working in the studio, it is easy to get a skewed perception, to derail from the global train of thought. By getting valuable feedback from the outside, we align ourselves once more with reality.
